Local normalisation using the empirical null for inspection of additive manufacturing using a single x-ray projection

### 2019-05-25 reports/paper1/paper.tex
Revise paper

\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{amssymb}
\usepackage{amsbsy}
\usepackage{graphicx}
\usepackage[outdir=./]{epstopdf}
\usepackage[round]{natbib} 
\usepackage{url}
\usepackage{subcaption}
\usepackage{hyperref}
\usepackage{hyphenat}
\usepackage{pdfpages}
\usepackage{MnSymbol} %udots
\usepackage{afterpage} %\afterpage{\clearpage}
\usepackage{siunitx} %for measurements

@@

\title{Local Normalisation using the Empirical Null for Inspection of Additive Manufacturing using X-Rays}
\date{2019}
\author{
  Sherman Lo \and Gregory Gibbons \and Thomas Nichols \and Julia Brettschneider \and Mark Williams \and Jason Warnett
}

@@

\begin{abstract}
X-ray computed tomography can be used for defect detection in additive manufacturing. The object is scanned at multiple angles to reconstruct the object in 3D space. To avoid this time consuming process, it was investigated whenever it is possible to detect defects based on a single scan. A 3D printed sample was manufactured with voids to see if they can be detected. The x-ray acquisition was compared with a simulation of that scan under the face of uncertainty by treating each pixel as a hypothesis test. The empirical null filter locally normalises each test statistic using robust estimators of the mean and deviation so that sensible inference was achieved.
\end{abstract}

@@

Quality control in additive manufacturing (or 3D printing) can be done using x-ray computed tomography (CT) \citep{thompson2016x}. The CT is compared to the computer aided design (CAD) so that voids and surface deviation can be measured in terms of position and size \citep{villarraga2015assessing, lee2015compliance, kim2016inspection}. The disadvantage of x-ray CT is that it involves calculations on the acquisition of hundreds of angles of the sample.

Speeding up the quality control process on the production line could be done by doing an inspection on a few numbers of x-ray images \citep{warnett2016towards}. These x-ray images are compared with a simulation of that scan using software called \texttt{aRTist} \citep{bellon2007artist, jaenisch2008artist, bellon2012radiographic}. \texttt{aRTist} can simulate x-ray acquisitions of the 3D printed sample given the specifications of the scan, such as the x-ray source, the x-ray detector and the computer aided design (CAD) of the 3D printed sample \citep{bellon2011simulation, deresch2012simulating}. Users of \texttt{aRTist} can align the simulated x-ray image to the real x-ray image using numerical methods.

A method was proposed to compare the x-ray image with \texttt{aRTist} by treating the simulation of \texttt{aRTist} as the ground truth. This was done by using two-tailed multiple hypothesis testing \citep{pearson1900on, neyman1933on, fisher1970statistical} controlling the false discovery rate (FDR) \citep{benjamini1995controlling, benjamini2010discovering}, treating each pixel as an individual test. However beforehand, the empirical null \citep{efron2004large} was used to do local normalisation on the test statistics. This was necessary because the simulation of \texttt{aRTist} do not match up perfectly with the x-ray image, producing incorrect inference.

An x-ray image of a 3D printed sample was obtained and compared with the \texttt{aRTist} simulation in an experiment. The procedure is shown in the methods section along with the description of the empirical null filter. In addition, the software development and simulation studies of the filter was discussed. The results from the simulation and the experiment are shown in the results section. The conclusion section summarises the study along with a discussion on further work.

@@

A ABS plastic cuboid (\SI{4}{\centi\metre} $\times$ \SI{4}{\centi\metre} $\times$ \SI{6}{\centi\metre}) with voids was purposefully manufactured to see if they can be detected. The CAD shown in Figure \ref{fig:inference_testObject} was manufactured using a \emph{Fortus} 3D printer. The voids were of various diameters \SI{2.4}{\milli\metre}, \SI{1.2}{\milli\metre}, \SI{0.6}{\milli\metre} and \SI{0.3}{\milli\metre}. 6 voids for each diameter were designed in the CAD. Voids with diameters \SI{2.4}{\milli\metre} and \SI{0.6}{\milli\metre} were regularly arranged, otherwise they were arranged irregularly. The precision of the manufacturing was in the order of $\pm\SI{0.1}{\milli\metre}$.

\begin{figure}
  \centering
  \includegraphics[width=0.35\textwidth]{../figures/inference/TestObject.png}
  \caption{CAD of a 3D cuboid with voids. The voids were of various diameters \SI{2.4}{\milli\metre}, \SI{1.2}{\milli\metre}, \SI{0.6}{\milli\metre} and \SI{0.3}{\milli\metre}. 6 voids for each diameter were designed in the CAD. Voids with diameters \SI{2.4}{\milli\metre} and \SI{0.6}{\milli\metre} were regularly arranged, otherwise they were arranged irregularly. The scale shown is approximate.}
  \label{fig:inference_testObject}
\end{figure}

The x-ray source used a tungsten filament with a copper filter. The current and voltage was set to \SI{250}{\micro\ampere} and \SI{80}{\kilo\volt} respectively. The exposure time was \SI{500}{\milli\second}. The x-ray detector is a \emph{Perkin Elmer XRD 1621 AN/CN} digital x-ray detector, producing a $2000\times 2000$ 16-bit image. Shading correction \citep{young2000shading, munzenmayer2003enhancing}, using a black image at \SI{0}{\kilo\volt} and a white image at \SI{80}{\kilo\volt}, were used to remove panel effects from the x-ray detector.

The 3D printed sample was scanned 20 times at a fixed angle. The 20 x-ray images were spilt into 2. 19 random images were held out. The remaining image was used to compare with \texttt{aRTist}. In the \texttt{aRTist} simulation, the software did a simulation as if the voids were not there.

@@

Two-tailed multiple hypothesis testing \citep{pearson1900on, neyman1933on, fisher1970statistical} was used to quantify the disagreement of each pixel between the scan and \texttt{aRTist}. A disagreement too big will classify that pixel as a positive result. A test statistic $Z_{x,y}$ for the $(x,y)$ positioned pixel was calculated for all pixels. This test statistic, together makes a $z$ image, is
\begin{equation}
  Z_{x,y} = 
  \dfrac{
    \text{scan}_{x,y} - \texttt{aRTist}_{x,y}
  }
  {
    \sqrt{\widehat{\variance}\left[\text{scan}_{x,y}\right]}
  }
\end{equation}
where $\widehat{\variance}\left[\text{scan}_{x,y}\right]$ is the estimated grey value variance of pixel $(x,y)$ in the scan.

The variance model, $\widehat{\variance}\left[\text{scan}_{x,y}\right]$ has a linear relationship between the variance and the grey value \citep{yang2010noise}. The fitting of the model was done using the held out replicated x-ray images of the 3D printed sample. These replicated x-ray images were manually segmented. This provided variance-mean data, where each pixel is a data point, and was used to fit the variance model. The model used was a gamma distributed generalised linear model \citep{nelder1972generalized, mccullagh1984generalized} with an identity link. The variance was predicted using the grey value in the \texttt{aRTist} simulation as the predictor variable when working out the test statistics.

@@

The empirical null filter was implemented using \texttt{ImageJ} \citep{abramoff2004image, schindelin2012fiji, schneider2012nih, perez2013image} by modifying the existing class \texttt{RankFilters}. It contains implementations of filters, such as the mean filter and median filter, using a circular kernel and multiple threads. Each thread filters a row in parallel.

@@

The larger defects were successfully highlighted by the hypothesis test. It can be seen that the empirical null mean did change face to face, resulting in a clear boundary set by the edges. This probably suggest that the contamination or inaccuracy from \texttt{aRTist} was face dependent.

@@

\begin{figure*}
  \centering
    \centerline{
      \begin{subfigure}[b]{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/inference/AllNullGaussianEmpirical_time.eps}
        \caption{Empirical null filter}
      \end{subfigure}
      \begin{subfigure}[b]{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/inference/AllNullGaussianMeanVar_time.eps}
        \caption{Mean variance null filter}
      \end{subfigure}
    }
  \caption{Timings when filtering a $256\times 256$ image. The mean variance null filter uses the sample mean and sample standard deviation to locally normalise the image. Note the y-axis change scale.}
  \label{fig:inference_timing}
\end{figure*}

There are a few strategies to accelerate the filter. The empirical null filter may be accelerated using GPUs \citep{yang2008parallel, hwu2011gpu, eklund2013medical}, however efforts to implement the filter in \texttt{CUDA} and \texttt{C++} is fruitless if there may exist a faster method. Instead, accuracy may be sacrificed for speed by only estimating the null parameters for a number of regularly spaced pixels, the remaining pixels then do estimation through interpolation. The problem is that the assumption of a slow varying null parameter is required much more because of the use of interpolation, this may cause bigger problems due to the face to face transition observed in the experiments. It was found that if a bad solution was found for a point, then that solution would spread its bad solution to neighbour pixels due to the interpolation.

@@

\section{Acknowledgements}
This work is funded by EPSRC grant numbers EP/K031066/1 and EP/L016710/1.

>>>>

\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{amssymb}
\usepackage{amsbsy}
\usepackage{graphicx}
\usepackage[outdir=./]{epstopdf}
\usepackage[round]{natbib} 
\usepackage{url}
\usepackage{subcaption}
\usepackage{hyperref}
\usepackage{hyphenat}
\usepackage{pdfpages}
\usepackage{MnSymbol} %udots
\usepackage{afterpage} %\afterpage{\clearpage}
\usepackage{siunitx} %for measurements
\usepackage{soul}%highlight changes

@@

\title{Local normalisation using the empirical null for inspection of additive manufacturing using a single x-ray projection}
\date{2019}
\author{
  Sherman Lo \and Gregory Gibbons \and Thomas Nichols \and Julia Brettschneider \and Mark Williams \and Jason Warnett
}

@@

\begin{abstract}
X-ray computed tomography can be used for defect detection in additive manufacturing. \hl{Typically, x-ray projections of an object are taken at a number of angles that are then reconstructed to create a 3D representation of the object inclusive of internal features. To avoid this time consuming process, it was investigated whenever it is possible to detect defects based on a single angular projection.} A 3D printed sample was manufactured with voids to see if they can be detected. The x-ray acquisition was compared with a simulation of that scan under the face of uncertainty by treating each pixel as a hypothesis test. The empirical null filter locally normalises each test statistic using robust estimators of the mean and deviation so that sensible inference was achieved.
\end{abstract}

@@

Quality control in additive manufacturing (or 3D printing) can be done using x-ray computed tomography (CT) \citep{thompson2016x}. The CT is compared to the computer aided design (CAD) so that voids and surface deviation can be measured in terms of position and size \citep{villarraga2015assessing, lee2015compliance, kim2016inspection}. The disadvantage of x-ray CT is that it involves the \hl{acquisition and reconstruction of thousands} of projections of the sample. Speeding up the quality control process on the production line could be done by doing an inspection on a \hl{fewer number of projections by sacrificing accuracy} \citep{warnett2016towards, brierley2018optimized}.

A method was proposed to compare a \hl{single projection with a simulation of that projection and treating it as the ground truth.} This was done by using two-tailed multiple hypothesis testing \citep{pearson1900on, neyman1933on, fisher1970statistical} controlling the false discovery rate (FDR) \citep{benjamini1995controlling, benjamini2010discovering}, treating each pixel as an individual test. Beforehand however, the empirical null \citep{efron2004large} was used to do local normalisation on the test statistics. This was necessary because the simulation of the projection did not match up perfectly, producing incorrect inference.

An x-ray \hl{projection} of a 3D printed sample was obtained and compared with the simulation in an experiment. The procedure is shown in the methods section along with the description of the empirical null filter. In addition, the software development and simulation studies of the filter was discussed. The results from the simulation and the experiment are shown in the results section. The conclusion section summarises the study along with a discussion on further work.

@@

An ABS plastic cuboid (\SI{40}{\milli\metre} $\times$ \SI{40}{\milli\metre} $\times$ \SI{60}{\milli\metre}) with voids was purposefully manufactured to see if they can be detected. The CAD shown in Figure \ref{fig:inference_testObject} was manufactured using a \emph{Fortus 400mc (Stratasys, US)} 3D printer. The voids were of diameters \SI{2.4}{\milli\metre}, \SI{1.2}{\milli\metre}, \SI{0.6}{\milli\metre} and \SI{0.3}{\milli\metre}. 6 voids for each diameter were designed in the CAD. Voids with diameters \SI{2.4}{\milli\metre} and \SI{0.6}{\milli\metre} were regularly arranged, otherwise they were arranged irregularly. The precision of the manufacturing was in the order of $\pm\SI{0.1}{\milli\metre}$.

\begin{figure}
  \centering
  \includegraphics[width=0.35\textwidth]{../figures/inference/TestObject.png}
  \caption{CAD of a 3D cuboid with voids. The voids were of diameters \SI{2.4}{\milli\metre}, \SI{1.2}{\milli\metre}, \SI{0.6}{\milli\metre} and \SI{0.3}{\milli\metre}. 6 voids for each diameter were designed in the CAD. Voids with diameters \SI{2.4}{\milli\metre} and \SI{0.6}{\milli\metre} were regularly arranged, otherwise they were arranged irregularly. The scale shown is approximate.}
  \label{fig:inference_testObject}
\end{figure}

X-ray projections were obtained using the \emph{Nikon XT H LC 225/320} x-ray CT scanner \emph{(Nikon Metrology, UK)}. The \SI{225}{\kilo\volt} source was used with a $2000\times2000$ pixel \emph{Perkin Elmer} detector consisting of \SI{200}{\micro\metre} pixels, separated by a distance of \SI{1870}{\milli\metre}. This object was placed on the manipulator, positioned to obtain a $5.7\times$ magnification resulting in an equivalent pixel size of \SI{35}{\micro\metre}. A voltage of \SI{80}{\kilo\volt} was used with a power of \SI{20}{\watt} resulting in a spot size of \SI{20}{\micro\metre} such that penumbra effects were negligible. 20 greyscale projections were acquired at an exposure time of \SI{500}{\milli\second}. A shading correction \citep{young2000shading, munzenmayer2003enhancing} was applied to each projection using a black (\SI{0}{\kilo\volt}) and white image (\SI{80}{\kilo\volt}) projection to remove intensity influences and variations in pixels of the detector.

The 3D printed sample was scanned 20 times at a fixed angle. The 20 x-ray projections were spilt into 2. 19 random projections were held out. The remaining projection was used to compare with the simulation using \emph{aRTist} \citep{bellon2007artist, jaenisch2008artist, bellon2012radiographic}. In the \emph{aRTist} simulation, the software did a simulation as if the voids were not there. Numerical methods were used to align the simulated x-ray image to the obtained x-ray projection.

@@

Two-tailed multiple hypothesis testing \citep{pearson1900on, neyman1933on, fisher1970statistical} was used to quantify the disagreement of each pixel between the scan and \emph{aRTist}. A disagreement too big will classify that pixel as a positive result. A test statistic $Z_{x,y}$ for the $(x,y)$ positioned pixel was calculated for all pixels. This test statistic, together makes a $z$ image, is
\begin{equation}
  Z_{x,y} = 
  \dfrac{
    \text{scan}_{x,y} - \emph{aRTist}_{x,y}
  }
  {
    \sqrt{\widehat{\variance}\left[\text{scan}_{x,y}\right]}
  }
\end{equation}
where $\widehat{\variance}\left[\text{scan}_{x,y}\right]$ is the estimated grey value variance of pixel $(x,y)$ in the scan.

The variance model, $\widehat{\variance}\left[\text{scan}_{x,y}\right]$ has a linear relationship between the variance and the grey value \citep{yang2010noise}. The fitting of the model was done using the held out replicated x-ray images of the 3D printed sample. These replicated x-ray images were manually segmented. This provided variance-mean data, where each pixel is a data point, and was used to fit the variance model. The model used was a gamma distributed generalised linear model \citep{nelder1972generalized, mccullagh1984generalized} with an identity link. The variance was predicted using the grey value in the \emph{aRTist} simulation as the predictor variable when working out the test statistics.

@@

The empirical null filter was implemented using \emph{ImageJ} \citep{abramoff2004image, schindelin2012fiji, schneider2012nih, perez2013image} by modifying the existing class \texttt{RankFilters}. It contains implementations of filters, such as the mean filter and median filter, using a circular kernel and multiple threads. Each thread filters a row in parallel.

@@

The larger defects were successfully highlighted by the hypothesis test. It can be seen that the empirical null mean did change face to face, resulting in a clear boundary set by the edges. This probably suggest that the contamination or inaccuracy from \emph{aRTist} was face dependent.

@@

\begin{figure*}
  \centering
    \centerline{
      \begin{subfigure}[b]{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/inference/AllNullGaussianEmpirical_time.eps}
        \caption{Empirical null filter}
      \end{subfigure}
      \begin{subfigure}[b]{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/inference/AllNullGaussianMeanVar_time.eps}
        \caption{Mean variance null filter}
      \end{subfigure}
    }
  \caption{Timings when filtering a $256\times 256$ image. The mean variance null filter uses the sample mean and sample standard deviation to locally normalise the image. Note that the $y$-axis changes scale. The box plot summarise 100 repeated measurements of the timings.}
  \label{fig:inference_timing}
\end{figure*}

There are a few strategies to accelerate the filter. The empirical null filter may be accelerated using GPUs \citep{yang2008parallel, hwu2011gpu, eklund2013medical}, however efforts to implement the filter in \emph{CUDA} and \emph{C++} is fruitless if there may exist a faster method. Instead, accuracy may be sacrificed for speed by only estimating the null parameters for a number of regularly spaced pixels, the remaining pixels then do estimation through interpolation. The problem is that the assumption of a slow varying null parameter is required much more because of the use of interpolation, this may cause bigger problems due to the face to face transition observed in the experiments. It was found that if a bad solution was found for a point, then that solution would spread its bad solution to neighbour pixels due to the interpolation.

@@

\section{Acknowledgements}
This work is funded by EPSRC grant numbers EP/K031066/1 (Inside-out: Statistical methods for Computed Tomography validation of complex structures in Additive Layer Manufacturing) and EP/L016710/1 (EPSRC and MRC Centre for Doctoral Training in Next Generation Statistical Science: The Oxford-Warwick Statistics Programme).
